---
title: "02402 - Statistics exercise week 2"
output: html_notebook
author: "Daniel F. Hauge"
---

All Exercise descriptions are available in the book at the course website: [Book](https://02402.compute.dtu.dk/enotes/book-IntroStatistics)

Inspirational material used:
- https://www.youtube.com/watch?v=8idr1WZ1A7Q
- https://www.youtube.com/watch?v=ZA4JkHKZM50




# 2.1 Discrete random variable

## a) 

```{r}
dbinom(4,10,0.6)
```
The probability of success for a single try is 60%. Trying 10 times, what is the probability that a success occurs 4 times. This is the binomial distribution, which is about 11,14767 %. ie. What is the chances to succeed 4 times out of 10 tries with 60% chance of success, where the results is independent of each other. 

That makes sense, as there would be the biggest chance of betting 6 successes out of 10 tries with 60% chance of success, and very low chance of getting 0 successes with 10 tries at 60% chance at success. That means gettign 4 successes out of 10 is a little off the expected value, meaning it is not the highest chance to occur as 6 succeses out of 10 would have.

## b)

Given the probability of succes at 60%, with 10 tries.

```{r}
lt6 <- pbinom(5,10,0.6) + pbinom(4,10,0.6) + pbinom(3,10,0.6) + pbinom(2,10,0.6) + pbinom(1,10,0.6)
lt5 <- pbinom(4,10,0.6) + pbinom(3,10,0.6) + pbinom(2,10,0.6) + pbinom(1,10,0.6)
gt4 <- 1 - (pbinom(4,10,0.6) + pbinom(3,10,0.6) + pbinom(2,10,0.6) + pbinom(1,10,0.6))

d<-c(lt6,lt5,gt4)
d
```
The probability of 5 or fewer succeses are about 60%.

the probability of 4 or fewer succeses are about 23,4%.

The probability of 5 or more successes are about 76%.

## c)

```{r}
dpois(4,3)
```
The mean is 3, meaning that 3 is the most likely observation for that given frame of observations. The poisson distribution looks at the probability of it being 4. The poisson distribution is calculating how likely a given event is based on known means. 0.168.. means that there is a 16% probability that the obersvations show 4. 

To better understand it, let the distribution be over number of cars driving by a road in a minute. The mean is 3, the poisson distribution can calculate the likelyhood that it will 4 be instead.


## d)
Here we just sum the probabilities

```{r}
lt6 <- ppois(5,3, lower.tail = TRUE)
lt5 <- 1 - ppois(4,3, lower.tail = FALSE) 
gt4 <- 1 - ppois(3,3, lower.tail = TRUE)

info <- c(lt6,lt5,gt4)
info

```
There is a 91% chance of the stochastic variable being less than 6.

There is a 81% chance of the stochastic variable being less than 5

There is a 35% chance of the stochastic variable being bigger than 4.

# 2.4 Consumer survey

## a)

```{r}
## Number of successes in the population
a <- 6
## Size of the population
N <- 20
## Number of draws
n <- 3
## Plot the pdf, note: parameters names are different in the R function
## Distribution of probabilities: dhyper(x=0:(n+1), m=a, n=N-a,k=n)
1 - phyper(0, a, N-a, n)
```
68% chance that no discrepancies ocurs.

# 2.5 Hay delivery quality

## a) 

```{r}
believed <- 2/20

s <- sample(c(0,1), 2000, replace=TRUE, c(18/20, 2/20))

mean(s)
var(s)
1- dbinom(0,20,2/20)

## Number of successes in the population
a <- 2
## Size of the population
N <- 20
## Number of draws
n <- 3
## Plot the pdf, note: parameters names are different in the R function
## Distribution of probabilities: dhyper(x=0:(n+1), m=a, n=N-a,k=n)
1 - phyper(0, a, N-a, n)

```
Mean is of infected bales are based on sample test approx 8%.

The variance is also 8%.

The probability of atleast one bale out of 3 checked in a batch of 20 with a expected likelihood of 2/20 bales is 28%.


## b)
```{r}

dbinom(0, 10, 0.01)
dbinom(0, 10, 0.1)

```
There is a 90% chance that no bales are infected in the 10 trials for a 1% infection rate.

There is a 35% chance that no bales are infected in the 10 trials for a 10% infection rate.

# 2.7 A fully automated production

```{r}
lambda <- 1.6
dpois(0:8, lambda)
1 - ppois(5, lambda)


## Number of realizations
# n <- 1000
## Simulate
# x <- rpois(n, lambda)
## Plot the empirical pdf
# plot(table(x)/n)
## Add the pdf to the plot
# lines(0:20, dpois(0:20,lambda), type="h", col="red")

```
The chances of there being more than 5 items in the control unit in a minute is approx 0.6% chance.

```{r}
lambda <- (1.6)*5

ppois(8, lambda)
```
There is a 59% chance that no more than 8 items arrive to the control unit within 5 minutes.


# 2.8 Call center staff

```{r}
averageCallsPerHour <- 180
averageCallsPerFiveMinutes <- averageCallsPerHour/12
lambda <- averageCallsPerFiveMinutes
# probability of 19 or less calls per 5 minutes. ( 1 - ppois) for probability of over exceeding 
1 - ppois(19, lambda)
```
There is a 12% probability that the call center will exceed its capacity in a random period of 5 minutes.


```{r}
lambda <- 15
# probability of 19 or less calls per 5 minutes.
ppois(25, lambda)
```
For the probability of not over exceeding, the capacity should be 25 or less calls per 5 minutes.
