---
title: "02402 - Statistics exercise week 3"
output: html_notebook
author: "Daniel F. Hauge"
---

All Exercise descriptions are available in the book at the course website: [Book](https://02402.compute.dtu.dk/enotes/book-IntroStatistics)





# 2.9 Continuous random variable

## a)
```{r}
library(lattice)
mean <- 0
sd <- 1
from <- 10
to <- 2
e4a <- seq(-4, 4, length = 10000)            # Data to set up out normal
e4b <- dnorm(e4a, mean, sd)

         xyplot(e4b ~ e4a,                   # Lattice xyplot
               type = "l",
               main = sprintf("Plot with: pnorm(2) = %s", pnorm(2)),
               panel = function(x,y, ...){
                   panel.xyplot(x,y, ...)
                   panel.abline( v = c(2), lty = 2)  #set z and lines

                   xx <- c(1, x[x>=-from & x<=to], to)         #Color area
                   yy <- c(0,   y[x>=-from & x<=to], 0) 
                   panel.polygon(xx,yy, ..., col='red')
               })
```
pnorm(2) descripes the probabilities of the next occurence being below 2, following a normal distribution.

```{r}
library(lattice)
m <- 1
sd <- 1
from <- 10
to <- 2
e4a <- seq(-4, 4, length = 10000)            # Data to set up out normal
e4b <- dnorm(e4a, m, sd)

         xyplot(e4b ~ e4a,                   # Lattice xyplot
               type = "l",
               main = sprintf("Plot with: pnorm(2,1,1) = %s", pnorm(2,1,1)),
               panel = function(x,y, ...){
                   panel.xyplot(x,y, ...)
                   panel.abline( v = c(2), lty = 2)  #set z and lines

                   xx <- c(1, x[x>=-from & x<=to], to)         #Color area
                   yy <- c(0,   y[x>=-from & x<=to], 0) 
                   panel.polygon(xx,yy, ..., col='red')
               })
```
```{r}
library(lattice)
m <- 1
sd <- 2
from <- 10
to <- 2
e4a <- seq(-4, 4, length = 10000)            # Data to set up out normal
e4b <- dnorm(e4a, m, sd)

         xyplot(e4b ~ e4a,                   # Lattice xyplot
               type = "l",
               main = sprintf("Plot with: pnorm(2,1,2) = %s", pnorm(2,1,2)),
               panel = function(x,y, ...){
                   panel.xyplot(x,y, ...)
                   panel.abline( v = c(2), lty = 2)  #set z and lines

                   xx <- c(1, x[x>=-from & x<=to], to)         #Color area
                   yy <- c(0,   y[x>=-from & x<=to], 0) 
                   panel.polygon(xx,yy, ..., col='red')
               })
```

## b)

```{r}
qnorm(pnorm(2))
```
It works like a reverse to pnorm. Meaning. Given a probability, where is that on the normal distribution?.
Meaning, if pnorm of 2 goes into qnorm, it just gives 2. As it kinda cancels each others out.


## c)
```{r}
library(lattice)
m <- 0
sd <- 1
from <- 10
to <- qnorm(0.975)
e4a <- seq(-4, 4, length = 10000)            # Data to set up out normal
e4b <- dnorm(e4a, m, sd)

         xyplot(e4b ~ e4a,                   # Lattice xyplot
               type = "l",
               main = sprintf("Plot with: qnorm(0.975) = %s", qnorm(0.975)),
               panel = function(x,y, ...){
                   panel.xyplot(x,y, ...)
                   panel.abline( v = c(to), lty = 2)  #set z and lines

                   xx <- c(1, x[x>=-from & x<=to], to)         #Color area
                   yy <- c(0,   y[x>=-from & x<=to], 0) 
                   panel.polygon(xx,yy, ..., col='red')
               })
```
At what quartile, or place does it include for the given probability 97,5%, on a standard normal distribution. 
It is approximately below 2.

```{r}
library(lattice)
m <- 1
sd <- 1
from <- 10
to <- qnorm(0.975,m,sd)
e4a <- seq(-4, 4, length = 10000)            # Data to set up out normal
e4b <- dnorm(e4a, m, sd)

         xyplot(e4b ~ e4a,                   # Lattice xyplot
               type = "l",
               main = sprintf("Plot with: qnorm(0.975, 1, 1) = %s", qnorm(0.975,m,sd)),
               panel = function(x,y, ...){
                   panel.xyplot(x,y, ...)
                   panel.abline( v = c(to), lty = 2)  #set z and lines

                   xx <- c(1, x[x>=-from & x<=to], to)         #Color area
                   yy <- c(0,   y[x>=-from & x<=to], 0) 
                   panel.polygon(xx,yy, ..., col='red')
               })
```
At what quartile, or place does it include for the given probability 97,5%, on a normal distribution, with mean = 1, basicly just shifted 1. 
It is approximately below 3. 
```{r}
library(lattice)
m <- 1
sd <- 2
from <- 10
to <- qnorm(0.975,m,sd)
e4a <- seq(-8, 8, length = 10000)            # Data to set up out normal
e4b <- dnorm(e4a, m, sd)

         xyplot(e4b ~ e4a,                   # Lattice xyplot
               type = "l",
               main = sprintf("Plot with: qnorm(0.975, 1, 2) = %s", qnorm(0.975,m,sd)),
               panel = function(x,y, ...){
                   panel.xyplot(x,y, ...)
                   panel.abline( v = c(to), lty = 2)  #set z and lines

                   xx <- c(1, x[x>=-from & x<=to], to)         #Color area
                   yy <- c(0,   y[x>=-from & x<=to], 0) 
                   panel.polygon(xx,yy, ..., col='red')
               })
```
At what quartile, or place does it include for the given probability 97,5%, on a normal distribution, with mean = 1 and standard deviation = 2. 
It is approximately below 5. 


# 2.10 The normal pdf
```{r}
library(lattice)
m <- 1
sd <- 2
e4a <- seq(-8, 8, length = 10000)            # Data to set up out normal
e4b <- dnorm(e4a, m, sd)

         xyplot(e4b ~ e4a,                   # Lattice xyplot
               type = "l",
               main = sprintf("normal dist"),
               panel = function(x,y, ...){
                   panel.xyplot(x,y, ...)
                   panel.abline( v = c(to), lty = 2)  #set z and lines

               })
```

## a)
The variance is not 2.

## b)
```{r}
library(lattice)
m <- 24
sd <- sqrt(16)
from <- 0
to <- 20
e4a <- seq(0, 50, length = 10000)            # Data to set up out normal
e4b <- dnorm(e4a, m, sd)

         xyplot(e4b ~ e4a,                   # Lattice xyplot
               type = "l",
               main = sprintf("P(x=<20) = pnorm(%s, %s, %s) = %s", to, m, sd, pnorm(to, m,sd)),
               panel = function(x,y, ...){
                   panel.xyplot(x,y, ...)
                 
                   xx <- c(1, x[x>=-from & x<=to], to)         #Color area
                   yy <- c(0,   y[x>=-from & x<=to], 0) 
                   panel.polygon(xx,yy, ..., col='red')

               })
```

```{r}
library(lattice)
m <- 24
sd <- sqrt(16)
from <- 29.5
to <- 100
e4a <- seq(0, 50, length = 10000)            # Data to set up out normal
e4b <- dnorm(e4a, m, sd)

         xyplot(e4b ~ e4a,                   # Lattice xyplot
               type = "l",
               main = sprintf("P(x > 29,5) = 1- pnorm(%s, %s, %s) = %s", from, m, sd, 1- pnorm(from, m,sd)),
               panel = function(x,y, ...){
                   panel.xyplot(x,y, ...)
                 
                   xx <- c(from, x[x>=from & x<=to], to)         #Color area
                   yy <- c(0,   y[x>=from & x<=to], 0) 
                   panel.polygon(xx,yy, ..., col='red')

               })
```

The desity of being exactly 23.8 is 0. Desity needs to be of a range


# 2.11 Computer chip control

## a)
```{r}
library(lattice)
m <- 54
sd <- 3
from <- (65-10)
to <- 1000
e4a <- seq(0, 100, length = 10000)            # Data to set up out normal
e4b <- dnorm(e4a, m, sd)

         xyplot(e4b ~ e4a,                   # Lattice xyplot
               type = "l",
               main = sprintf("P(x > %s) = 1- pnorm(%s, %s, %s) = %s", from, from, m, sd, 1- pnorm(from, m,sd)),
               panel = function(x,y, ...){
                   panel.xyplot(x,y, ...)
                 
                   xx <- c(from, x[x>=from & x<=to], to)         #Color area
                   yy <- c(0,   y[x>=from & x<=to], 0) 
                   panel.polygon(xx,yy, ..., col='red')

               })

```


To save less than 10 miliseconds on the new machine.It needs to take longer than 55 seconds. As this would be more than 10 seconds from the expected.

##b) 
Following a normal distribution, the mean is 54 and 3 miliseconds standard deviation. For 100 chips.

# 2.12 Concrete items
```{r}
library(lattice)
m <- 3000
sd <- 3
from <- (2993)
to <- 3007
e4a <- seq(2990, 3010, length = 10000)            # Data to set up out normal
e4b <- dnorm(e4a, m, sd)

         xyplot(e4b ~ e4a,                   # Lattice xyplot
               type = "l",
               main = sprintf("1 - P(%s <= X <= %s) = (pnorm(%s, %s, %s)*2) = %s", from, to, from, m, sd, (pnorm(from, m,sd)*2)),
               panel = function(x,y, ...){
                   panel.xyplot(x,y, ...)
                 
                   xx <- c(from, x[x>=from & x<=to], to)         #Color area
                   yy <- c(0,   y[x>=from & x<=to], 0) 
                   panel.polygon(xx,yy, ..., col='red')

               })
```
Not the red area. 1,9% error rate.

## b)
```{r}
qnorm(0.99,2900, 100)
?
```



# 2.13 Online statistic video views

```{r}
VisitersYear <- 110000
VisistersDay <- VisitersYear/365
VisistersHour <- VisistersDay/24
VisisterHalfHour <- VisistersHour/2
VisistersQuarter <- VisisterHalfHour/2
ppois(0, VisisterHalfHour)
ppois(0, VisistersQuarter)
```
There is a 0,18% chance that there are no views in a ghiven half hour.
There is a 4,3% chance you'd have to wait more than 15 min.
