---
title: "02402 - Statistics exercise 1.1: Infant birth weight"
output: html_notebook
author: "Daniel F. Hauge"
---

All Exercise descriptions are available in the book at the course website: [Book](https://02402.compute.dtu.dk/enotes/book-IntroStatistics)

Exercise description is available in the book: [Exercise 1.1](https://02402.compute.dtu.dk/enotes/book-IntroStatistics#DV%3aexc%3ainfant-birth-weight)


## Init

```{r}
x <- c(2474,2547,2830,3219,3429,3448,3677,3872,4001,4116)
y <- c(2844,2863,2963,3239,3379,3449,3582,3926,4151,4356)
```

## a) 

```{r}
totalX <- 0

for (i in x){
  totalX <- totalX + i
}

meanX <- totalX / length(x)
meanX

varianceX <- 0
for (i in x) {
  varianceX <- (varianceX + (i - meanX)^2)
}
varianceX <- varianceX / (length(x)-1)
varianceX


standardDeviation <- sqrt(varianceX)
standardDeviation
```

The mean is the average, or central value seen from a perspective of the value.

Variance is the metric that describe how far apart the values are from the central value. Meaning, how far apart the data is spread. A high variance, means there are a lot of different values that are very different from the central value. A low variance means that the data is very centered around the central value. Variance is the total amount of spread amount there is.

Standard deviation is the value that the typical point of data deviates from the mean. 

## b)

```{r}
mean(y)
var(y)
sd(y)
```
Male are on average more heavy than females. And also the females are deviating more, more occurrences and farther from the central values.

## c)
```{r}
quantile(y)
quantile(x)
```
```{r}
boxplot(x,y)
```

## d)
There a female extreme small value and a male extreme big value.

## e)
```{r}
sd(x)/mean(x)
sd(y)/mean(y)
```

