---
title: "02402 - Statistics exercise 1.3: Cholesterol"
output: html_notebook
author: "Daniel F. Hauge"
---

All Exercise descriptions are available in the book at the course website: [Book](https://02402.compute.dtu.dk/enotes/book-IntroStatistics)

Exercise description is available in the book: [Exercise 1.3](https://02402.compute.dtu.dk/enotes/book-IntroStatistics#DV%3aexc%3acholesterol)


## Init

```{r}
before <- c(9.1, 8.0, 7.7, 10.0, 9.6, 7.9, 9.0, 7.1, 8.3, 9.6, 8.2, 9.2, 7.3, 8.5, 9.5)
after <- c(8.2, 6.4, 6.6, 8.5, 8.0, 5.8, 7.8, 7.2, 6.7, 9.8, 7.1, 7.7, 6.0, 6.6, 8.4)
```

## a) 


```{r}
median(before)
median(after)

```
## b)
```{r}
sd(before)
sd(after)
```
## c)
```{r}
cov(before, after)
```
## d)

```{r}
cor(before, after)

```
## e)

```{r}
difs <- before - after
mean(difs)
var(difs)
sd(difs)
```
```{r}
boxplot(difs)
```

## f)

The mean is shown to be lower for after. The mean of each observation is 1.2, which is evident that in the total cholesterol level of all patients in the sample is lowered after the procedure. The standard deviation is not very big, meaning many of the observations are very closely packet, which means that no outlandish data is present.
